SOL Filamentary transport: update from joint AUG-TCV MST1 experiment

### 2018-01-24 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to TeX file

\begin{frame}{Current scan at constant q$_{95}$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
      \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
      \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
      \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG: Divertor neutral density exhibits still
          the same behavior is considered as a function of greenwald fraction
        \item<5|only@5> For AUG upstream and target profiles exhibit
          the same behavior with flattening observed at large values
          of $\Lambda_{div}$. TCV actually even at high value of
          density no sign of upstream profile flattening \alert{even
            at very large values of $\Lambda_{div}$}
        \item<6|only@6> This is due to the fact we did not reach
          divertor detachment which \alert{seems necessary for
            upstream profile modification}  
        \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<8|only@8> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<9|only@9> And for TCV this is true even at high value of $\Lambda_{div}$

      \end{itemize}
    \end{column}
  \end{columns}

>>>>

\begin{frame}{Current scan at constant q$_{95}$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
      \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
      \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
      \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG: Divertor neutral density exhibits still
          the same behavior is considered as a function of greenwald fraction
        \item<5|only@5> For AUG upstream and target profiles exhibit
          the same behavior with flattening observed at large values
          of $\Lambda_{div}$. TCV actually even at high value of
          density no sign of upstream profile flattening \alert{even
            at very large values of $\Lambda_{div}$}
        \item<6|only@6> This is due to the fact we did not reach
          divertor detachment which \alert{seems necessary for
            upstream profile modification}  
        \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<8|only@8> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<9|only@9> And for TCV this is true even at high value of $\Lambda_{div}$
      \end{itemize}
    \end{column}
  \end{columns}
%% H-Mode same fueling
\begin{frame}{H-Mode compare fueling with/wo
      cryopump}
    \Fontvi
  \vspace{-1cm}
  \begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
    \only<3>{
    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
    \end{tikzonimage}}
  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}}
  \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
    \item<1|only@1> Same fueling but with cryo-pumps. \alert{To check role
        of neutral density in H-Mode}
      \item<1|only@1> H-5 density is different and remain constant, both
        divertor and midplane pressure are reduced (to 1/3
        approximately) no sign of detachment
      \item<2|only@2> Different ELMy regimes reached with reduced size and
        increased frequency without the cryopumps
      \item<3|only@3> Also with this amount of fueling weaker indication of SOL
        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
      \item<4|only@4> Inter-ELM resolved profile suggest a flattening even
        with the cryompumps still even though $\Lambda_{div}$ is
        marginal above 1 only in the near SOL
       \item<5|only@5> Without the cryopumps, we reached flatter
         profiles with comparable inter-ELM resolved blob-size. This
         indicates strong neutral pressure effects in determining
         upstream profiles
      \end{itemize}
  \end{column}
\end{columns}
%% H-Mode different torus
\begin{frame}{Matching scenarios with cryo-pumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
    \centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
    \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34281}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> To match similar edge density and divertor pressure
        and to reach the same level of detachment we increase the
        fueling by almost a factor of 3, increasing also the rate. In
        addition to that we also increase substantially the N
        puffing. \alert{Degraded H-Mode reached earlier in density
          without the cryopumps}
      \item<2|only@2> Similar ELMy behavior obtained during the density ramp  
      \item<3|only@3> Now the scenario suggest a strong profile flattening
        even with the cryopumps
       \item<4|only@4> Inter-ELM resolved Li-Be profiles confirm this with
         shoulder formed with similar strength even with the cryopumps
         in operation.
         \item<5|only@5> Both size and $\lambda_n$ closer with/wo the cryopumps 
       \end{itemize}
  \end{column}
\end{columns}
